A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-07-14 src/paper.tex
Web application section

The front controller architectural design pattern~\cite{Buschmann2007} is employed to centralize requests processing in a single component. Each second screen client sends requests to and receives responses from a single URL, what simplifies application development.

- Web application

@@

>>>>

\subsection{Web Application}
\label{ssub_web_application}

The web applications, which can be hosted in the AHI, comprises the business logic of the second screen application. The content that is presented in the second screen client can be requested through HTTP requests to web services designed for this purpose. In addition, the data captured by second screen clients in the iTV environment can also be sent to the CP by using HTTP requests.

The HTTP requests handling is carried out by using the front controller architectural design pattern~\cite{Buschmann2007}. It is employed to centralize requests processing in a single component, which facilitates the design and implementation of services for different second screen clients. As a result, client applications can access the same service even when they are developed for different operating systems in different programming languages.

@@

The second screen devices are used to interact with the content being watched in the TV terminal.

- Presentation of the content

- Capture of viewers interactions (using the WEB service)
